API design for machine learning software: experiences from the scikit-learn project

### 2013-06-28 paper.tex
copyedit/trim double parameter grid part, again

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, \ldots X_p$, called features, and
some output variable $Y$. A sample is then defined as a pair of
values $([x_1, \ldots, x_p]^\mathrm{T}, y)$ of these variables. A widely used
representation of a dataset, a collection of
such samples, is a pair of matrix with numerical values: one for the input
values and one for the output values. Each row of these matrix
corresponds to one sample of the dataset and each column to one variable of
the problem.

@@

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
Note that, in the above example, two distinct hyper-parameter grids are
considered. This is because it only makes sense to search for \texttt{gamma}
when \texttt{kernel} is set to \texttt{"rbf"}.
An SVM with a linear kernel accepts a $\gamma$ parameter, but ignores it,
so using a single parameter grid would waste computing time
trying out effectively equivalent settings.
Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, just like any other classifier:
it delegates the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator
(optionally after re-fitting it on the whole training set).

>>>>

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a supervised learning task, the goal is to find a mapping
from input variables $X_1, \ldots X_p$, called features, to
some output variables $Y$. A sample is then defined as a pair of
values $([x_1, \ldots, x_p]^\mathrm{T}, y)$ of these variables. A widely used
representation of a dataset, a collection of
such samples, is a pair of matrices with numerical values: one for the input
values and one for the output values. Each row of these matrices
corresponds to one sample of the dataset and each column to one variable of
the problem.

@@

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
In this example, two distinct hyper-parameter grids are
considered for the linear and radial basis function (RBF) kernels;
an SVM with a linear kernel accepts a $\gamma$ parameter, but ignores it,
so using a single parameter grid would waste computing time
trying out effectively equivalent settings.
Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, just like any other classifier:
it delegates the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator
(optionally after re-fitting it on the whole training set).
